Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
Minor style changes.

The experimental evaluation in section~\ref{experimental-results} outlines
a very positive assessment of \tool over a diverse set of real-world
benchmarks. Nevertheless, the set of benchmarks is limited within the
scope of this paper and \tool's performance may not generalise to other
benchmark scenarios. This can be addressed by expanding the benchmark set
based on available literature in future experiments.

>>>>

The experimental evaluation in section~\ref{experimental-results} outlines
a very positive assessment of \tool over a diverse set of real-world
benchmarks. Nevertheless, this set of benchmarks is limited within the
scope of this paper and \tool's performance may not generalise to other
benchmark scenarios. This can be addressed by expanding the benchmark set
based on available literature in future experiments.
